---
title: "Exercise1 Manuel Waller"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Hello, this is a document to summarize my results for exercise 1. First I created 100 random values of a lognormal distribution with mu=1 and sigma=0.25. Those values were then directly stored under the objectname "Datasample".
```{r}
Datasample <- rlnorm(100, 1, 0.25)
```
This randomly generated datasample looks as follows:
```{r}
Datasample
```

Mean and variance of this randomly generated datasample were then calculated with the following command-lines:
```{r}
mean(Datasample)
```
```{r}
var(Datasample)
```
The mean of the Datasample is 2.810455 and the variance 0.638443.

Finally, I generated a histogram to get an idea of the samples distribution:
```{r}
 hist(Datasample, freq = F, ylim=c(0, 0.8), breaks = seq(from=1, to=6, by=0.2))
```

Another task was to generate a histogram of the sample-values to show the distribution on the log-scale. I understood that it was expected to generate a histogram with a log-scale y-axis. However, I couldn`t come up with a quick solution to that, so I simply calculated the logs of the values of the datasample and showed those calculated logs in a "normal" histogram. I hope this will do for the moment...
```{r}
LogDatasample <- log(Datasample)
```
```{r}
hist(LogDatasample, breaks = seq(from=0, to=2, by=0.1))
```

